---
title: "Wilcoxon Project"
author: "Emmanuel Asante"
date: "10/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(rsample)
set.seed(785363)
```


## Issue 1

Generate samples from Poisson distribution. I will take a sample from Poisson distributions of two different rates and conduct a test of hypothesis on the two samples. Do this for 1000 simulated pairs of samples.

```{r, warning=F, message=F}

# Generate two poisson samples whose sizes are not necessarily the same
sample_1 <- rpois(10 + rbinom(1, size = 20, prob = 0.5), lambda = 10)
sample_2 <- rpois(10 + rbinom(1, size = 20, prob = 0.5), lambda = 10)

#Test the hypothesis that they both have the same mean(come from the same distribution)
wilcox.test(sample_1, sample_2)


# Create a dataframe to contain all the samples and computed values
wilcox_table <- data_frame(index = 1:1000)

# set number of simulations to 1000
n_sim <- 1000

wilcox_table <- wilcox_table %>% 
  mutate(sample_1 = rerun(n_sim, rpois(30 + rbinom(1, size = 20, prob = 0.5), lambda = 10)),
         sample_2 = rerun(n_sim, rpois(30 + rbinom(1, size = 20, prob = 0.5), lambda = 10)),
         wilcox_pvalue = flatten_dbl(map2(sample_1, sample_2, ~wilcox.test(.x, .y)$p.value)))

# Type 1 error rate of the test on the samples of the same poisson population

mean(wilcox_table$wilcox_pvalue<=0.05)

```

Add a column to indicate that the nULLL HYPOTHESIS IS rejected or not

```{r}
wilcox_table <- wilcox_table %>% 
  mutate(Reject = ifelse(wilcox_pvalue <= 0.05, 1, 0))
```


Can I put all of that into a function so that I can simulate 10000 of such dataframes and get the type 1 error rates? Then I will plot the histogram for the type 1 error rate(hopefully it follows some distribution?)

First lets try to make the function

```{r}
# set number of simulations to 1000
n_sim <- 1000

wilcox_table <- wilcox_table %>% 
  mutate(sample_1 = rerun(n_sim, rpois(30 + rbinom(1, size = 20, prob = 0.5), lambda = 10)),
         sample_2 = rerun(n_sim, rpois(30 + rbinom(1, size = 20, prob = 0.5), lambda = 10)),
         wilcox_pvalue = flatten_dbl(map2(sample_1, sample_2, ~wilcox.test(.x, .y)$p.value)))


# Write a function for One table

wilcox_one_table <- function(table_length = 1000, sample_from = rpois, ..., alpha = 0.05){
  wilcox_table <- data_frame(index = 1:table_length)
  wilcox_table <- wilcox_table %>% 
  mutate(sample_1 = rerun(table_length, sample_from(30 + rbinom(1, size = 20, prob = 0.5), ...)),
         sample_2 = rerun(table_length, sample_from(30 + rbinom(1, size = 20, prob = 0.5), ...)),
         wilcox_pvalue = flatten_dbl(map2(sample_1, sample_2, ~wilcox.test(.x, .y, exact = FALSE)$p.value)), 
         Reject = ifelse(wilcox_pvalue <= alpha, TRUE, FALSE))
  output <- list(type_1_error_rate = mean(wilcox_table$Reject), one_table = wilcox_table)
  print(output)
}

aa <- wilcox_one_table(table_length = 1000, sample_from = rpois, alpha = 0.05, lambda = 20)

##### Write function
# Probably use append

wilcox_error_rate <- function(number_tables = 1000, distribution = rpois, ...){
  
}

```

